Gafo-cc data processing

### 2022-07-28 analysis/gafo-cc-data-processing.Rmd
extended hierarchical model

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(prettyR) # for describe()
library(jsonlite) # for reading in json files
library(stringr)
library(eeptools)
library(lubridate) # for date handling
library(readxl)
library(readODS)

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"), 
  ) %>%
  select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
```

```{r demographics}
raw_demographics_namibia <- bind_rows(
  read_xlsx("../../raw_data/gafo-cc/namibia/Data FarmSix 2022.xlsx", sheet = 1)%>%mutate(ID = paste0("H",str_pad(ID, 7, pad = "0"))),
  read_xlsx("../../raw_data/gafo-cc/namibia/Data Khwe 2022.xlsx", sheet = 1)%>%mutate(ID = paste0("K",str_pad(ID, 7, pad = "0")))%>%rename(sex = `...7`)
  )

tidy_demographics_namibia <- raw_demographics_namibia %>% 
  mutate(
    ageInYears = as.numeric(difftime(TestDate,BirthDate, units = "days")/365.25),
  ) %>%
  rename(subjID = ID) %>% 
  select(-c(`First Name`, Name, BirthDate, TestDate, Comment))%>% 
  rename_all(tolower)%>%
  filter(!is.na(ageinyears))
```

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"), 
  ) %>%
  mutate(subjID = as.character(subjID),
         subjID = ifelse(subjID == "VcyYgGQx", "VcyYgFQx", subjID),
         subjID = ifelse(subjID == "R9V7qHrx", "R9v7qHrx", subjID),
         subjID = ifelse(subjID == "QZJvSwfQ","QZJvSwftQ",  subjID),
         subjID = ifelse(subjID == "TSPeVFYf", "tSPeVFYf", subjID),
         subjID =as.factor(subjID))%>%
  select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)

@@

```{r read_data}
# get all .json files
files <- list.files("../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/JSONs/", pattern = "*.json",recursive = T)

# convert json files to tibbles
raw_data_nigeria <- tibble()
for (f in files) {
  jf <- paste("../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/JSONs/", f, sep = "")
  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"),
    subjID = as.character(subjID),
    subjID = ifelse(subjID == "nlger002", "niger002", subjID)
  ) %>%
  select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
```

```{r demographics}
raw_demographics_nigeria <- bind_rows(
  read_xlsx("../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/gafo-cc-nigeria-participants.xlsx", sheet = 1)
  )

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali")
  ) %>%
  select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
```

@@

```{r}
data_zambia <- tidy_demographics_zambia%>%
  left_join(tidy_data_zambia%>%rename_all(tolower),by = c("subjid"))%>%
  mutate(community = "chimfunshi_kumwenda")
```

@@

data_nigeria$younger_children
```

@@

>>>>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(prettyR) # for describe()
library(jsonlite) # for reading in json files
library(stringr)
library(eeptools)
library(lubridate) # for date handling
library(readxl)
library(readODS)
library(truncnorm)

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"), 
  ) #%>% select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)

```{r demographics}
raw_demographics_namibia <- bind_rows(
  read_xlsx("../../raw_data/gafo-cc/namibia/GaFo Data Haikom 2022.xlsx", sheet = 1)%>%mutate(ID = paste0("H",str_pad(ID, 7, pad = "0")))%>%mutate(site = Community, Community = "hai||om"),
  read_xlsx("../../raw_data/gafo-cc/namibia/Data Khwe 2022.xlsx", sheet = 1)%>%mutate(ID = paste0("K",str_pad(ID, 7, pad = "0")))%>%rename(Sex = `...7`)%>%mutate(site = Community, Community = "khwe")
  )

tidy_demographics_namibia <- raw_demographics_namibia %>% 
  mutate(
    ageInYears = as.numeric(difftime(TestDate,BirthDate, units = "days")/365.25),
  ) %>%
  rename(subjID = ID) %>% 
  select(-c(`First Name`, Name, BirthDate, TestDate, Comment))%>% 
  rename_all(tolower)%>%
  filter(!is.na(ageinyears))

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"), 
  ) %>%
  mutate(subjID = as.character(subjID),
         subjID = ifelse(subjID == "VcyYgGQx", "VcyYgFQx", subjID),
         subjID = ifelse(subjID == "R9V7qHrx", "R9v7qHrx", subjID),
         subjID = ifelse(subjID == "QZJvSwfQ","QZJvSwftQ",  subjID),
         subjID = ifelse(subjID == "TSPeVFYf", "tSPeVFYf", subjID),
         subjID =as.factor(subjID))#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)

@@

```{r read_data}
# get all .json files
files <- list.files("../../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/JSONs/", pattern = "*.json",recursive = T)

# convert json files to tibbles
raw_data_nigeria <- tibble()
for (f in files) {
  jf <- paste("../../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/JSONs/", f, sep = "")
  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"),
    subjID = as.character(subjID),
    subjID = ifelse(subjID == "nlger002", "niger002", subjID)
  ) #%>% select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
```

```{r demographics}
raw_demographics_nigeria <- bind_rows(
  read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/gafo-cc-nigeria-participants.xlsx", sheet = 1)
  )

read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/gafo-cc-nigeria-participants.xlsx", sheet = 1)

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali")
  ) #%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
```

@@

```{r}
data_zambia <- tidy_demographics_zambia%>%
  left_join(tidy_data_zambia%>%rename_all(tolower),by = c("subjid"))%>%
  mutate(community = "chimfunshi")
```

@@

@@

# Data for model

```{r}
mdata <- data%>%
  filter(community == "leipzig" | community == "akure",
         voiceover == F)%>%
  mutate(agecentered = ageinyears - min(ageinyears))%>%
  select(-c(screen,touchscreen.x, household, children, younger_children, sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, touchscreen.y , os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status))

write(toJSON(mdata), file = "../model/model_data/gafo-cc-model-data.json")

mdata%>%
  filter(is.na(agecentered))

mdata%>%
  filter(trialnr == 5)%>%
  select(subjid,agecentered)
```

```{r}
mdata_small <- mdata%>%
  filter(subjid %in% c("VcyYgFQx", "k1mQYc2K", "niger007","niger057"))

write(toJSON(mdata_small), file = "../model/model_data/gafo-cc-model-data-small.json")
```

```{r}
prior <- dtruncnorm(seq(from = 0, to = 2900, by = 20), a = 1, b = 2920, mean = 1450, sd = 100)

length(prior)

write(toJSON(prior, digits = 4, use_signif = TRUE), file = "../model/model_data/centerBias_extended.json")
```
